The FAIRification of research in real-world evidence: A practical introduction to reproducible analytic workflows using Git and R

### 2023-11-22 manuscript/manuscript.qmd
explicitly point out that we refer to the RStudio IDE

In this section, we want to give a technical introduction on how Git and remote repositories can be used in RWE studies. For the following examples, we focus on workflows utilizing R/RStudio ([https://posit.co/download/rstudio-desktop/](https://posit.co/download/rstudio-desktop/https://posit.co/download/rstudio-desktop/)) and GitHub (<https://github.com/>) as a remote repository, although the general concepts are fairly similar and easily transferable to other programming languages and remote repository providers, respectively. We will show examples for both command line interface (CLI) prompts as well as for RStudio's integrated GUI. For more details, we refer to the book *Pro Git* by Chacon and Straub.[@chacon2014pro]

>>>>

In this section, we want to give a technical introduction on how Git and remote repositories can be used in RWE studies. For the following examples, we focus on workflows utilizing R/the RStudio integrated development environment (IDE) GUI ([https://posit.co/download/rstudio-desktop/](https://posit.co/download/rstudio-desktop/https://posit.co/download/rstudio-desktop/)) and GitHub (<https://github.com/>) as a remote repository, although the general concepts are fairly similar and easily transferable to other programming languages and remote repository providers, respectively. We will show examples for both command line interface (CLI) prompts as well as for RStudio's integrated GUI. For more details, we refer to the book *Pro Git* by Chacon and Straub.[@chacon2014pro]
